Verifying Demonstrations

### 2019-02-27 paper/verifiability-analysis.tex
Clarifies effect of other DB properties in security analysis
Emphasize that witness is trusted by verifier

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed at the location when the proof share was created.
In essence, the witness performs distance bounding to ensure Alice is close to 
them, this is then propagated to the verifier through the signature and trust 
in the witness's honesty.
Alice has three options:
\begin{enumerate*}
\item\label{spatial-DF} relay her communication with an honest witness through 
  a conspirator,
\item\label{spatial-forge} forge a witness signature for the proof,
\item corrupt a witness to issue a proof although neither might be present at 
  the location.
\end{enumerate*}

>>>>

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed at the location when the proof share was created.
In essence, the witness performs distance bounding to ensure Alice is close to 
them, this is then propagated to the verifier through the signature and founded 
on trust (remember that the witness is trusted by the verifier).
Alice has three options:
\begin{enumerate*}
\item\label{spatial-DF} relay her communication with an honest witness through 
  a conspirator,
\item\label{spatial-forge} forge a witness signature for the proof,
\item corrupt a witness to issue a proof although neither might be present at 
  the location.
\end{enumerate*}
